Lineage Analysis of CRISPR and shRNA Screens

### 2018-09-05 lineages_18Q3.Rmd

```{r}
crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
# write.table(crispr_data[, c("Hugo_Symbol", "Broad_ID", "Score", "Primary.Disease", "primary_tissue", "Mutation_Status")], file = "~/Desktop/crispr_data_select.tsv", quote = FALSE, sep = "\t")
```

@@

Distribution of scores across cell lines and primary tissues. Each data point represents a single cell line.
```{r fig.height=4, fig.width=12}
ceres_summ <- crispr_data %>% group_by(primary_tissue) %>% summarize(Max = max(Score),
                                                                     Min = min(Score))
score_summ_plot <- ggplot(data = crispr_data, aes(x = primary_tissue, color = primary_tissue)) +
  geom_boxplot(mapping = aes(y = Score), outlier.shape = NA) +
  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Min)) +
  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Max)) +
  scale_y_continuous(breaks = seq(-4, 6, by = 1), labels = seq(-4, 6, by = 1)) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1), legend.position = "none") +
  labs(x = "Primary Tissue", y = "CERES Score")

# ggsave(filename = "./plots_18Q3/crispr/ceres_score_summ_plot.pdf", plot = score_summ_plot, width = 12, height = 4, device = "pdf")
```

@@

maf_ccl_annot_plot <- ggplot(data = maf_ccl_annot, aes(x = primary_tissue, y = n, color = primary_tissue)) +
  geom_jitter(alpha = 0.8, size = 1, position = position_jitter(w = 0.25)) +
  scale_y_continuous(breaks = seq(0, 9000, by = 1000), labels = seq(0, 9000, by = 1000)) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1), legend.position = "none") +
  labs(x = "Primary Tissue", y = "Number of Mutations")

# ggsave(filename = "./plots_18Q3/crispr/maf_ccl_annot_plot.pdf", plot = maf_ccl_annot_plot, width = 12, height = 4, device = "pdf")
```

@@

```{r fig.height=3, fig.width=6}
wilcox_gene_plot <- ggplot(data = crispr_signif, aes(x = p.adj)) +
  geom_histogram(breaks = seq(0, 1, by = 0.025), fill = "darkslategray3", color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  coord_cartesian(ylim = c(0, 4500)) +
  scale_y_continuous(breaks = seq(0, 4500, by = 500), labels = formatC(seq(0, 4500, by = 500), format = "d")) +
  stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")

ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 10, height = 5, device = "pdf")
```

@@

```{r fig.height=3, fig.width=6}
wilcox_gene_tissue_plot <- ggplot(data = crispr_signif_tissue, aes(x = p.adj)) +
  geom_histogram(breaks = seq(0, 1, by = 0.025), fill = "darkslateblue", color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  coord_cartesian(ylim = c(0, 55000)) +
  scale_y_continuous(breaks = seq(0, 55000, by = 5000), labels = formatC(seq(0, 55000, by = 5000), format = "d")) +
  stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")

ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_gene_tissue_plot, width = 10, height = 5, device = "pdf")
```

@@

chm_all_plot <- Heatmap(chm_scores, name = "CERES Score",
        bottom_annotation = chm_annot_list,
        bottom_annotation_height = unit(5, "in"),
        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
        row_title = "Genes", column_title = "Cancer Cell Lines",
        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        row_title_gp = gpar(fontsize = 30, fontface = "bold"),
        row_names_gp = gpar(fontsize = 5),
        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
        column_names_gp = gpar(fontsize = 5),
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(2, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

pdf("./plots_18Q3/crispr_heatmap_euclidean_all.pdf", width = 50, height = 50, paper = "special")
draw(chm_all_plot, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
dev.off()
```

@@

pdf("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.pdf", width = 50, height = 50, paper = "special")
draw(chm_all_plot_cgc, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
dev.off()
```

@@

>>>>

```{r}
crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
# write.table(crispr_data, file = "~/Desktop/crispr_data.tsv", quote = FALSE, sep = "\t")
```

@@

Distribution of scores across cell lines and primary tissues. Each data point represents a single cell line.
```{r fig.height=4, fig.width=12}
ceres_summ <- crispr_data %>% group_by(primary_tissue) %>% summarize(Max = max(Score),
                                                                     Min = min(Score))
score_summ_plot <- ggplot(data = crispr_data, aes(x = primary_tissue, color = primary_tissue)) +
  geom_boxplot(mapping = aes(y = Score), outlier.shape = NA) +
  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Min)) +
  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Max)) +
  scale_y_continuous(breaks = seq(-4, 6, by = 1), labels = seq(-4, 6, by = 1)) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1), legend.position = "none") +
  labs(x = "Primary Tissue", y = "CERES Score")
score_summ_plot
# ggsave(filename = "./plots_18Q3/crispr/ceres_score_summ_plot.pdf", plot = score_summ_plot, width = 12, height = 4, device = "pdf")
```

@@

maf_ccl_annot_plot <- ggplot(data = maf_ccl_annot, aes(x = primary_tissue, y = n, color = primary_tissue)) +
  geom_boxplot(outlier.shape = NA, fill = NA) +
  geom_jitter(alpha = 0.7, size = 1, position = position_jitter(w = 0.25)) +
  scale_y_continuous(breaks = seq(0, 9000, by = 1000), labels = seq(0, 9000, by = 1000)) +
  theme(axis.ticks.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), legend.position = "none") +
  labs(x = "Primary Tissue", y = "Number of Mutations")
maf_ccl_annot_plot
# ggsave(filename = "./plots_18Q3/crispr/maf_ccl_annot_plot.pdf", plot = maf_ccl_annot_plot, width = 12, height = 4, device = "pdf")
```

```{r fig.height=8, fig.width=12}
ggsave(filename = "./plots_18Q3/crispr/score_mut_summ.pdf", plot = grid.draw(rbind(ggplotGrob(maf_ccl_annot_plot), ggplotGrob(score_summ_plot), size = "first")), width = 12, height = 8, device = "pdf")
```

@@

```{r fig.height=4, fig.width=8}
wilcox_gene_plot <- ggplot(data = crispr_signif) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3",), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  coord_cartesian(ylim = c(0, 4500)) +
  scale_y_continuous(breaks = seq(0, 4500, by = 500), labels = formatC(seq(0, 4500, by = 500), format = "d")) +
  #stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_gene_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
```

@@

```{r fig.height=4, fig.width=8}
wilcox_gene_tissue_plot <- ggplot(data = crispr_signif_tissue) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3",), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  scale_y_continuous(breaks = seq(0, 50000, by = 5000), labels = formatC(seq(0, 50000, by = 5000), format = "d")) +
  #stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_gene_tissue_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_gene_tissue_plot, width = 8, height = 4, device = "pdf")
```

@@

chm_all_plot <- Heatmap(chm_scores, name = "CERES Score",
        bottom_annotation = chm_annot_list,
        bottom_annotation_height = unit(5, "in"),
        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
        row_title = "Genes", column_title = "Cancer Cell Lines",
        col = colorRamp2(c(min(chm_scores), 0, max(chm_scores)), c("purple4", "white", "seagreen4")),
        na_col = "black",
        row_title_gp = gpar(fontsize = 30, fontface = "bold"),
        row_names_gp = gpar(fontsize = 5),
        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
        column_names_gp = gpar(fontsize = 5),
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(2, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

pdf("./plots_18Q3/crispr_heatmap_euclidean_all.pdf", width = 50, height = 50, paper = "special")
draw(chm_all_plot, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
dev.off()

png("./plots_18Q3/crispr_heatmap_euclidean_all.png", width = 50, height = 50, units = "in", res = 96)
draw(chm_all_plot, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
dev.off()
```

@@

pdf("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.pdf", width = 50, height = 50, paper = "special")
draw(chm_all_plot_cgc, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
dev.off()

png("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.png", width = 50, height = 50, units = "in", res = 96)
draw(chm_all_plot_cgc, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
dev.off()
```

@@

## Report 2 plot

```{r}
sig_genes <- c("KRAS", "TP53", "NRAS", "BRAF", "PIK3CA", "PTEN", "CTNNB1")
crispr_sig_genes <- filter(crispr_data, Hugo_Symbol %in% sig_genes)
crispr_sig_genes$Hugo_Symbol <- factor(crispr_sig_genes$Hugo_Symbol, levels = c("KRAS", "TP53", "NRAS", "BRAF", "PIK3CA", "PTEN", "CTNNB1"))
```

```{r fig.height=18, fig.width=5}
crispr_color <- as.character(crispr_sig_genes$Color)
names(crispr_color) <- crispr_sig_genes$Mutation_Status

# Mutation status
plot_mut <- ggplot(data = crispr_sig_genes, aes(x = Mutation_Status, y = Score, color = Mutation_Status)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha = 0.3, size = 0.7, position = position_jitter(w = 0.05)) +
  facet_wrap(~ Hugo_Symbol, nrow = 7, scales = "free_y") +
  scale_color_manual(values = crispr_color) +
  geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
  theme_light() +
  theme(legend.position = "none") +
  labs(x = "Mutation Status", y = "CERES Score",
       title = "Mutation Status")
# plot_mut

# Copy number
plot_cn <- ggplot(data = crispr_sig_genes, aes(x = Copy_Number, y = Score, color = Mutation_Status)) +
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "lm", size = 0.5) +
  scale_color_manual(values = crispr_color) +
  facet_wrap(~ Hugo_Symbol, nrow = 7, scales = "free") +
  stat_cor(method = "pearson", show.legend = FALSE, label.x.npc = "right", label.y.npc = "top") +
  theme_light() +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  labs(y = "CERES Score", color = "Mutation Status",
       x = "Theoretical Copy number", title = "Copy Number")
# plot_cn

# Gene expression
plot_ge <- ggplot(data = crispr_sig_genes, aes(x = RPKM_log2, y = Score, color = Mutation_Status)) +
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "lm", size = 0.5) +
  facet_wrap(~ Hugo_Symbol, nrow = 7, scales = "free_y") +
  scale_color_manual(values = crispr_color) +
  stat_cor(method = "pearson", show.legend = FALSE, label.x.npc = "left", label.y.npc = "top") +
  theme_light() +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  labs(y = "CERES Score", color = "Mutation Status",
       x = "Gene Expression [log2(RPKM)]",
       title = "Gene Expression")
# plot_ge
```

```{r fig.height=18, fig.width=15}
grid.newpage()
grid.draw(cbind(ggplotGrob(plot_mut), ggplotGrob(plot_ge), ggplotGrob(plot_cn), size = "last"))

ggsave(filename = "./plots_18Q3/crispr/omics_sig_genes.pdf", plot = grid.draw(cbind(ggplotGrob(plot_mut), ggplotGrob(plot_ge), ggplotGrob(plot_cn), size = "last")), width = 15, height = 18, device = "pdf")
```
